\documentclass[12pt,a4]{article}


\usepackage{a4wide}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{url}
\usepackage[breaklinks=true]{hyperref}
%\usepackage[colorlinks=true]{hyperref}
\addtolength{\textwidth}{2cm}
\addtolength{\oddsidemargin}{-1cm}
\addtolength{\textheight}{2cm}
\addtolength{\topmargin}{-2cm}

\newcommand{\provbfh}{\texttt{proVFBH}\xspace}
\newcommand{\provbfhincl}{\texttt{proVFBH-inclusive}\xspace}
\newcommand{\hoppet}{\texttt{hoppet}\xspace}
\title{\texttt{proVBFH-inclusive v.2.0.2} manual}

\begin{document}
\maketitle

This document provides a short documentation for the \provbfhincl code.
%---------------------------------------------------------------------
\section{Credits}
The \provbfh program was developed by Matteo Cacciari, Fr\'ed\'eric
Dreyer, Alexander Karlberg, Gavin Salam and Giulia Zanderighi and is
based on
\begin{itemize}
  \item M.~Cacciari, F.~A.~Dreyer, A.~Karlberg, G.~P.~Salam and G.~Zanderighi,
  %``Fully Differential Vector-Boson-Fusion Higgs Production at Next-to-Next-to-Leading Order,''
  Phys.\ Rev.\ Lett.\  {\bf 115} (2015) no.8,  082002
  % doi:10.1103/PhysRevLett.115.082002
  [arXiv:1506.02660 [hep-ph]],
\item F.~A.~Dreyer and A.~Karlberg,
  %``Vector-Boson Fusion Higgs Production at Three Loops in QCD,''
  Phys.\ Rev.\ Lett.\  {\bf 117} (2016) no.7,  072001
  % doi:10.1103/Phys\-RevLett.117.072001
  [arXiv:1606.00840 [hep-ph]].
\end{itemize}

When using results at next-to-next-to-next-to-leading order (N$^3$LO), the
original references on third order coefficient functions should be
cited as well
\begin{itemize}
\item A.~Vogt, S.~Moch and J.~A.~M.~Vermaseren,
  %``The Three-loop splitting functions in QCD: The Singlet case,''
  Nucl.\ Phys.\ B {\bf 691} (2004) 129
  % doi:10.1016/j.nuclphysb.2004.04.024
  [hep-ph/0404111].
\item S.~Moch, J.~A.~M.~Vermaseren and A.~Vogt,
  %``The Longitudinal structure function at the third order,''
  Phys.\ Lett.\ B {\bf 606} (2005) 123
  % doi:10.1016/j.physletb.2004.11.063
  [hep-ph/041.2.1].
\item J.~A.~M.~Vermaseren, A.~Vogt and S.~Moch,
  %``The Third-order QCD corrections to deep-inelastic scattering by photon exchange,''
  Nucl.\ Phys.\ B {\bf 724} (2005) 3
  % doi:10.1016/j.nuclphysb.2005.06.020
  [hep-ph/0504242].
\item S.~Moch, M.~Rogal and A.~Vogt,
  %``Differences between charged-current coefficient functions,''
  Nucl.\ Phys.\ B {\bf 790} (2008) 317
  % doi:10.1016/j.nuclphysb.2007.09.022
  [arXiv:0708.3731 [hep-ph]].
\end{itemize}

Finally, when evaluating cross sections for di-Higgs production the following reference should be cited
\begin{itemize}
\item F.~A.~Dreyer and A.~Karlberg,
%``Vector-Boson Fusion Higgs Pair Production at N$^3$LO,''
Phys. Rev. D \textbf{98} (2018) no.11, 114016
%doi:10.1103/PhysRevD.98.114016
[arXiv:1811.07906 [hep-ph]].
%83 citations counted in INSPIRE as of 10 Oct 2022
\end{itemize}
%----------------------------------------------------------------------
\section{Installation/dependencies}
To run \provbfhincl, you will need an installation of the following packages:
\begin{itemize}
\item \texttt{hoppet}:
  \url{https://github.com/hoppet-code/hoppet}. At least v.1.3.0.
\item \texttt{LHAPDF}: \url{http://lhapdf.hepforge.org/}.
\end{itemize}
With these installed, \provbfhincl can be compiled by going to the base
directory and running
\begin{verbatim}
 ./configure [options]
 make
\end{verbatim}
Available options in the \texttt{configure} script can be accessed
through the \texttt{--help} or \texttt{-h} argument, as well as being
described in the \texttt{INSTALL} text file.

We suggest that the references for \texttt{hoppet} and \texttt{LHAPDF}
are also cited when using our program.

%----------------------------------------------------------------------
\section{Setting up a run}
To run \provbfhincl, you can simply call the executable
\texttt{provbfh\_incl} created by the installation steps above.
%
All parameters are passed as command line options, with the full list
of settings detailed in the section below, or accessible in
\texttt{src/parameters.f90}.
%
Since executing the code will produce several files, the recommended
usage is to start individual runs in dedicated subfolders.

An example setup:
\begin{verbatim}
 mkdir nlo-14tev; cd $_
 ../provbfh_incl -nlo -sqrts 14000 -iseed 2
\end{verbatim}
This will produce three files, two files \texttt{grids\_0002.dat} and
\texttt{grids\_0002.top} containing the grid and an output file
\texttt{xsct\_nlo\_seed0002.dat} containing the results of the run.
%
Different seed numbers and orders in
$\alpha_s$ can be executed in the same location, as they will result
in distinct output files.

% ----------------------------------------------------------------------
\section{Dihiggs production}
To run \provbfhincl for dihiggs production, one needs to compile the
\texttt{provbfhh\_incl} program with
\begin{verbatim}
 make provbfhh_incl
\end{verbatim}
which can then be executed exactly like the single Higgs program to
calculate the total cross section in VBF Higgs pair production.
% ----------------------------------------------------------------------
\section{Input parameters}
All accessible parameters can be specified as command line arguments.

The available options, and their default value (in {\bf bold}), are:
\begin{itemize}
\item\texttt{-lo, -nlo, -nnlo, {\bf -n3lo}}: Order in $\alpha_s$.
  
\item\texttt{-sqrts} {\bf 13600}: Center-of-mass energy in GeV.

\item\texttt{-scale-choice} {\bf 1}: Scale choice to use, with the options
  \begin{itemize}
  \item 0: Fixed scale at $\mu_0^2=m^2_h$.
  \item 1: Vector boson momentum $\mu_0^2(Q_i^2)=Q^2_i=-q_i^2$.
  \item 2: Common scale given by $\mu_0^2(Q_1, Q_2)=Q_1 Q_2$.
  \item 3: 
    $\mu_0^2(p_{t,H}) = \frac{m_H}{2} \sqrt{\left(\frac{m_H}{2}\right)^2
      + p_{t,H}^2}$ from 1506.02660.
  \end{itemize}

\item\texttt{-xmuf} {\bf 1.0}: Factor $x_{\mu_F}$ multiplying the
  factorisation scale $\mu_F = x_{\mu_F} \mu_0$.

\item\texttt{-xmur} {\bf 1.0}: Factor $x_{\mu_R}$ multiplying the
  renormalisation scale $\mu_R = x_{\mu_R} \mu_0$.

\item\texttt{-pdf} {\bf PDF4LHC21\_40}: Choice of PDF set (by name).

\item\texttt{-nmempdf} {\bf 0}: Member of the PDF.

\item\texttt{-mh} {\bf 125.}: Higgs mass.

\item\texttt{-hwidth} {\bf 0.00402964}: Higgs width.
  
\item\texttt{-mw} {\bf 80.398}: $W$ mass.

\item\texttt{-wwidth} {\bf 2.141}: $W$ width.

\item\texttt{-mz} {\bf 91.187}: $Z$ mass.

\item\texttt{-zwidth} {\bf 2.4952}: $Z$ width.

\item\texttt{-nf} {\bf 5}: number of quark flavours.
  
\item\texttt{-mt} {\bf 172.4}: top mass.

\item\texttt{-mb} {\bf 4.75}: bottom mass.
  
\item\texttt{-readingrid}: Use available grid if possible.

\item\texttt{-higgsbreitwigner}: Use a Breit-Wigner propagator for the higgs.

\item\texttt{-higgsmasswindow} {\bf 30.}: Number of width to integrate around the BW peak.
  
\item\texttt{-ncall1} {\bf 100000}: Number of calls for the initialisation of the integration grid.

\item\texttt{-itmx1} {\bf 3}: Number of iterations for the grid initialisation.
  
\item\texttt{-ncall2} {\bf 100000}: Number of calls for evaluating the integral.

\item\texttt{-itmx2} {\bf 3}: Number of iterations for the integration.

\item\texttt{-iseed} {\bf 10}: Random seed.

\item\texttt{-pdfuncert}: Compute PDF uncertainties on the fly. Significantly increases computation time (scales linearly with the number of PDF members). Also computes $\alpha_S$ uncertainty if this is included in the PDF.

\item\texttt{-alphasuncert}: Separates the PDF and $\alpha_S$ uncertainty on the printout.

\item\texttt{-3scaleuncert}: Compute 3 point (ie symmetric) scale variation.

\item\texttt{-7scaleuncert}: Compute 7 point scale variation.

\end{itemize}
\end{document}
